%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Connor}{Mowry}{%\urlstyle{same}\url{http://crcmowry.github.io} \\

LinkedIn:// \href{https://www.linkedin.com/in/crcmowry}{\custombold{crcmowry}} |
\href{mailto:crcmowry@gmail.com}{crcmowry@gmail.com} | (412) 848-4497
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.39\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Carnegie Mellon University}
\descript{BS in Computer Science}
\location{Expected May 2021 | Pittsburgh, PA \\ Cum. GPA: 3.73 %\\ Major GPA: 4.0}
}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links} 
%LinkedIn:// \href{https://www.linkedin.com/in/crcmowry}{\custombold{crcmowry}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\custombold{(Asterisk denotes course in progress)} \\
Algorithm Design and Analysis (15-451) \\
Foundations of PL (15-312) \\
Probability and Computing (15-259)

Intro to Computer Systems (15-213) \\
Data Structures and Algos (15-210) \\
Multidimensional Calculus (21-268) \\
Hype for Types (98-317) \\

Great Theoretical Ideas in CS (15-251) \\
More Great Ideas in TCS (15-252) \\
Intro to Functional Programming (15-150) \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming Languages}
\vspace{\topsep}
C/C++ \(\bullet\)
Python \(\bullet\)
OCaml \(\bullet\)
C\# \(\bullet\)
Java

Javascript/Typescript \(\bullet\)
HTML \& CSS

\sectionsep

\subsection{Tools \& Frameworks}
\vspace{\topsep}
Play \(\bullet\)
Docker \(\bullet\)
Flask

React Native \(\bullet\)
Git \(\bullet\)
PostgreSQL

Bootstrap \(\bullet\)
Bash \(\bullet\)
\LaTeX \(\bullet\)
Vim
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.60\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Microsoft}
\descript{| Software Engineer Intern}
\location{May 2018 – Aug 2018 | Pittsburgh, PA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
    \item Implemented feature allowing IT admins to prevent users from removing
        or wiping corporate managed devices.
\end{tightemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\runsubsection{Carnegie Mellon University}
\descript{| 15-210 Teaching Assistant}
\location{May 2018 – Aug 2018 | Pittsburgh, PA}
\begin{tightemize}
    \item Lead recitations, held office hours, helped create new labs, and graded
        assignments and exams for Par and Seq Data Structures and Algos.
\end{tightemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\runsubsection{Software Engineering Institute}
\descript{| Developer Intern }
\location{May 2018 – Aug 2018 | Pittsburgh, PA}
\begin{tightemize}
    \item Built from scratch a Java Play Framework web application to easily configure and monitor the security state and data of IoT devices.
\end{tightemize}

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\runsubsection{Elliance}
\descript{| Developer Intern }
\location{June 2017 – Aug 2017 | Pittsburgh, PA}
\begin{tightemize}
    \item Developed \href{http://www.pittsburgh.net/}{Pittsburgh.net} mobile application for using React Native to help the user browse and save local Pittsburgh events.
\end{tightemize}

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities} 
\runsubsection{ScottyLabs}
\descript{| Former Directory of Technology}
\location{Nov 2017 – Present}
\begin{tightemize}
    \item Manage club's technical direction and oversee all technical projects.
    \item Gave a talk on Git covering basic usage and then taking an extensive
        look at branching.
    \item Led a workshop on back-end development at WebDevWeekend, an
        educational event introducing students to web dev fundamentals.
    \item Planned TartanHacks, Carnegie Mellon's largest hackathon of over 300 students, which is held by ScottyLabs.
\end{tightemize}

\sectionsep

\runsubsection{Delta Tau Delta}
\descript{| Directory of Academic Affairs}
\location{Jan 2018 – Present}
\begin{tightemize}
    \item Meet with struggling members to help them achieve academic success.
\end{tightemize}

\sectionsep

\runsubsection{AC Mellon Club Soccer}
\descript{| Goalkeeper}
\location{Sep 2017 – December 2018}
\begin{tightemize}
    \item Play goalkeeper on Carnegie Mellon's nationally competitive club soccer team.
    \item Competed in national tournament against the best collegiate club teams
        in the U.S. (Dec 2018).
    \item Competed in regional tournament (Oct 2017).
\end{tightemize}

\sectionsep

\end{minipage} 
\end{document}
